### 2010-12-06 docs/tex/result.tex
All results updated...

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
	\caption[Population distribution of generated mimicry rings (initialized with 2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey-generated-prey}
\end{figure}

@@

\section{Initial configuration with only unpalatable species}
\label{sec:init-conf-only-unp}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all unpalatable.}
\label{tab:config-table-4-prey-unpalatable}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{30}} \\ \cline{2-4}
  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all palatable.}
\label{tab:config-table-4-prey-palatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime-9k-4Prey-p}
	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-4Prey-p}
	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{|c|}{10} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species unpalatable.}
\label{tab:config-table-1-prey-unpalatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime8k-1-unp}
	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:plot-1-prey-unp}
\end{figure}

@@

\subsection{Palatable}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{|c|}{8} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.03}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species palatable.}
\label{tab:config-table-1-prey-palatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime9k-1-p}
	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
	\label{fig:plot-1-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize8k-1Prey-p}
	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
	\label{fig:ringSize8k-1-Prey-p}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-2Prey-generated-prey}
	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey-generated-prey}
\end{figure}

@@

\section{Initial configuration with only unpalatable species}
\label{sec:init-conf-only-unp}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule55  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all unpalatable.}
\label{tab:config-table-4-prey-unpalatable}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule110}} 
  																									& 150 & \multicolumn{2}{|c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{|c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule190}}& 150 & \multicolumn{2}{|c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{5000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species all palatable.}
\label{tab:config-table-4-prey-palatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-4Prey-p}
	\caption[Population distribution of mimicry rings (4 prey species all palatable)]{Population distribution of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:plot-4-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-4Prey-p}
	\caption[Number of mimicry rings (4 prey species all palatable)]{Number of mimicry rings, initialized with 4 prey species all palatable.}
	\label{fig:ringSize8k-4-Prey-p}
\end{figure}

@@

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{|c|}{10} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species unpalatable.}
\label{tab:config-table-1-prey-unpalatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime8k-1Prey-unp}
	\caption[Population distribution of mimicry rings (1 prey species unpalatable)]{Population distribution of mimicry rings, initialized with 1 prey species unpalatable.}
	\label{fig:plot-1-prey-unp}
\end{figure}

@@

\subsection{Palatable}
\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|c|l|c|}
  \hline
   														&\multicolumn{3}{|c|}{Prey configuration} 																	
   														& \multicolumn{2}{|c|}{Predator configuration} \\ \hline
  Population 									& Rule30 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{images/CARule30}} 
  																									& 216 & \multicolumn{2}{|c|}{8} \\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{|c|}{100}  & \multicolumn{2}{|c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{|c|}{1000} & \multicolumn{2}{|c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{|c|}{0.05} & \multicolumn{2}{|c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{|c|}{0.5}  & \multicolumn{2}{|c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{|c|}{2000}							& \multicolumn{2}{|c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{|c|}{} 						    & \multicolumn{2}{|c|}{500} \\ \hline
  \multirow{2}{*}{Memory Configuration} & \multicolumn{3}{|c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{|c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 1 prey species palatable.}
\label{tab:config-table-1-prey-palatable}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.40]{images/simTime10k-1Prey-p}
	\caption[Population distribution of mimicry rings (1 prey species palatable)]{Population distribution of mimicry rings, initialized with 1 prey species palatable.}
	\label{fig:plot-1-prey-p}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.50]{images/ringSize10k-1Prey-p}
	\caption[Number of mimicry rings (1 palatable prey species)]{Number of mimicry rings, initialized with 1 palatable prey species.}
	\label{fig:ringSize8k-1-Prey-p}
\end{figure}
